Verification of Petri Nets Using Linear Programming

### 2014-02-03 paper/workspace/main.tex
Pushing the preamble.

\documentclass{article}

\usepackage{amsmath}
\usepackage[usenames,dvipsnames]{color}
\usepackage{listings}
\usepackage[a4paper, top=2cm, bottom=3cm, left=2cm, right=2cm]{geometry}
\usepackage{graphicx}

\usepackage{tikz}
\usetikzlibrary{arrows,shapes,shapes.multipart,shapes.geometric,
	snakes,automata,backgrounds,petri,calc,positioning}

\newcommand{\bfc}{{\sc Bfc}}
\newcommand{\mist}{{\sc Mist}}
\newcommand{\iic}{{\sc IIC}}
\newcommand{\pnerf}{{\sc Pnerf}}
\newcommand{\zthree}{{\sc Z3}}
\newcommand{\ttt}[1]{\texttt{#1}}

\tikzstyle{place}=[circle,thick,draw=black!75,fill=white!20,
  	minimum size=6mm]
\tikzstyle{red place}=[place,draw=red!75,fill=red!20]
\tikzstyle{blue place}=[place,draw=blue!75,fill=blue!20]
\tikzstyle{transition}=[rectangle,thick,draw=black!75,
  	fill=black!20,minimum size=4mm]

\tikzstyle{state}=[draw, ellipse, aspect=2]
\tikzstyle{action}=[draw, rectangle, align=center]
\tikzstyle{decision}=[draw, diamond, aspect=2, align=center]
\tikzstyle{print}=[draw, trapezium, trapezium left angle=70, trapezium right angle=-70]
\tikzstyle{every path}=[draw, ->, >=stealth, shorten >=2pt, shorten <=2pt]

@@

\title{Report on a Safety Checker for Petri nets}
\author{Philipp Meyer \and Rusl\'{a}n Ledesma-Garza}
% \institute{Technische Universit\"at M\"unchen}
\date{Mon Nov 25 14:24:10 CET 2013}

>>>>

\documentclass{llncs}

\input{preamble}

@@

\ifthenelse{\equal{\isDraft}{false}}{
  \title{Verification of Petri Nets Using Linear Programming}
  \author{
    Javier Esparza\inst{1}
    \and
    Ruslán Ledesma-Garza\inst{1}
    \and
    Rupak Majumdar\inst{2}
    \and
    Philipp Meyer\inst{1}
    \and
    Filip Niksic\inst{2}
  }
  \institute{
    Technische Universität München
    \and
    MPI-SWS, Kaiserslautern and Saarbrücken
  }
  \maketitle
}{}
